The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH]

### 2024-02-15 paper/paper.qmd
Added and cleaned a new data set for follow up to the main experiment.

#Acquiring cleaned data from output folder
online_cleaned <-
   read_csv(
    file = here("data/analysis_data/online_cleaned.csv"))
wwoh_data <-
  read_csv(
    file = here("data/analysis_data/main_cleaned.csv"))

@@

## Measurement and collection
The "1st Online Survey Clean" will only be used to conduct analysis on the support of married Saudi Arabian men on women working outside of home. Therefore, its selection process is not extremely extensive. The qualifying characteristics are marriage status (married) and age (18-35). This survey was conducted nationally and anonymously. The other aspects of this survey is not further discussed as the data will not be used in this paper.

@@

@tbl-samplemain shows what the cleaned data for the main experiment looks like.
```{r}
#| echo: false
#| label: tbl-samplemain
#| tbl-cap: Sample of Cleaned Main Experiment Data of Saudi Arabian Men on WWOH
wwoh_data |> slice(1:5) |> kable()

@@

Before manipulating the data into graphs and tables to test these claims, we can first understand the cleaned data better with summary statistics.

```{r}
#| echo: false
#| label: tbl-summ
#| tbl-cap: Summary Statistics on Men Who Participated in the Main Experiment
summary_stats <- wwoh_data |>
  group_by(condition2) |>
  summarize(
    Observations = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
  ) |>
  bind_rows()|>
  mutate(group = c("Control", "Treatment"))

@@

summary_all <- wwoh_data |>
  summarize(
    Total = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100)

@@

As seen in @tbl-summ above, there are less than 500 data points present in the cleaned data. From these data points, we can test

```{r}
#| echo: false
#| label: fig-time
#| fig-cap: Density Histogram of Percentage Wedge
histogram <- wwoh_data |>
  mutate(percentage_wedge = outside_wedge/30*100)

p <- ggplot(histogram, aes(x = percentage_wedge)) + 
  geom_histogram(aes(y = after_stat(density)), binwidth = 8, fill = "green", alpha = 0.6, color = "black") + 
  labs(
       x = "Percentage Wedge Value",
       y = "Density",
       caption = "Distribution of the difference between beliefs on what percentage people support WWOH and actual percentage of people that support WWOH. The values were calculated as (participants guess about percent of session participants that agree with WWOH - the actual percentage of participants that agree with WWOH") + 
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, face = "italic", size = 10),
        plot.caption.position = "plot") +
  scale_x_continuous(limits = c(-100, 100))

print(p)
```
In @fig-time, we plotted the “wedge” between the participant’s belief in what percentage of others would support WWOH and how many participants actually supported WWOH. In assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts. On average, this wedge is observed to be a 24 percentage points difference, aligning very similarly with the conclusions drawn from the original paper @paper.

@@

# Additional data details

## Posterior predictive check

>>>>

#Acquiring cleaned data from output folder
online_cleaned <-
   read_csv(
    file = here("data/analysis_data/online_cleaned.csv"))
main_cleaned <-
  read_csv(
    file = here("data/analysis_data/main_cleaned.csv"))

@@

## Measurement and collection
"1st Online Survey Clean" will only be used to conduct analysis on the support of married Saudi Arabian men on women working outside of home. Therefore, its selection process is not extremely extensive. The qualifying characteristics are marriage status (married) and age (18-35). This survey was conducted nationally and anonymously. The other aspects of this survey is not further discussed as the data will not be used in this paper.

@@

@tbl-samplemain shows what the cleaned data for the main experiment looks like.
```{r}
#| echo: false
#| label: tbl-samplemain
#| tbl-cap: Sample of Cleaned Main Experiment Data of Saudi Arabian Men on WWOH
main_cleaned |> slice(1:5) |> kable()

@@

The first claim can be easily explored using the cleaned national online survey data with its variable on the participant's support of WWOH.

```{r}
#| echo: false
#| label: fig-wwoh
#| fig-cap: Support of Young Married Men in Saudi Arabia of WWOH
online_cleaned |> 
  ggplot(aes(x = c_outside_self)) +
  geom_bar() +
  theme_minimal() +
  labs(x = "Support of WWOH (Y = 1/N = 0)", y = "Frequency of Responses" )

```
@fig-wwoh confirms that the majority of young married men in Saudi Arabia do support women working outside of home. Out of the 728 observations, around 600 chose in favour that "In my opinion, women should be allowed to work outside of the home" @paper. This signifies that the first claim is accurate.

Starting from the second claim, we will be using the main experiment data. Before manipulating it into graphs and tables, we can first understand the cleaned data better with summary statistics.

```{r}
#| echo: false
#| label: tbl-summ
#| tbl-cap: Summary Statistics on Men Who Participated in the Main Experiment
summary_stats <- main_cleaned |>
  group_by(condition2) |>
  summarize(
    Observations = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
  ) |>
  bind_rows()|>
  mutate(group = c("Control", "Treatment"))

@@

summary_all <- main_cleaned |>
  summarize(
    Total = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100)

@@

As seen in @tbl-summ above, there are less than 500 data points present in the cleaned data. From these data points, we can test the claim that married men massively underestimate the level of support from other men in their communities. The surveys from the main experiment asked the participants about their predictions of how many others in the group of 30 (from 0 to 29) of many they know of, would support WWOH. The percentage difference between their beliefs and the actual calculated number is shown as wedges in @fig-time. This graph shows the distribution of the difference between beliefs on what percentage people support WWOH and actual percentage of people that support WWOH. The values were calculated as (participants guess about percent of session participants that agree with WWOH - the actual percentage of participants that agree with WWOH).

```{r}
#| echo: false
#| label: fig-time
#| fig-cap: Density Histogram of Percentage Wedge
histogram <- main_cleaned |>
  mutate(percentage_wedge = outside_wedge/30*100)

p <- ggplot(histogram, aes(x = percentage_wedge)) + 
  geom_histogram(aes(y = after_stat(density)), binwidth = 8, fill = "green", alpha = 0.6, color = "black") + 
  labs(
       x = "Percentage Wedge Value",
       y = "Density") + 
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, face = "italic", size = 10),
        plot.caption.position = "plot") +
  scale_x_continuous(limits = c(-100, 100))

print(p)
```
In @fig-time, from assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts. On average, this wedge is observed to be a 24 percentage points difference, aligning very similarly with the conclusions drawn from the original paper @paper. Thus, the second claim of that married men massively underestimate the level of support from other men in their communities is further substantiated.

@@
